---
title: "Exploratory Visualizations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}

require(dplyr)
require(ggplot2)
require(openintro)
require(lattice)
require(stringr)

# Fix our directory if we're one too high
if(str_detect(getwd(), ".*Analysis.*$")) {
  setwd("../")
}

source(file.path("Analysis", "analyzeAttentionBehavior.R"))
```

```{r, include = FALSE}
# Fix our directory if we're one too high
if(str_detect(getwd(), ".*Analysis.*$")) {
  setwd("../")
}

clean_path = file.path("Data", "CleanCSV")
drunk1 = read.csv(file.path(clean_path, "20130612090533.csv"))
sober1 = read.csv(file.path(clean_path, "20130529091650.csv"))
```

```{r, include = FALSE}
drunkEventOccur = filter(drunk1, SCC.MenuSearch != 0)
soberEventOccur = filter(sober1, SCC.MenuSearch != 0)
drunkEventNotOccur = filter(drunk1, SCC.MenuSearch == 0)
soberEventNotOccur = filter(sober1, SCC.MenuSearch == 0)
```

### Examining proportion of items being looked at by dosing condition and whether the event was occurring
```{r}
barplot(table(drunkEventOccur$Combined.Item.Name)/nrow(drunkEventOccur)*100, ylim=c(0,100), ylab = "Percent", xlab = "object index number", main = "Intoxicated (THC:2.630 and BAC: 0.065) and Artist Search Task Occuring")

barplot(table(drunkEventNotOccur$Combined.Item.Name)/nrow(drunkEventNotOccur)*100, ylim=c(0,100), ylab = "Percent", xlab = "object index number", main = "Intoxicated (THC:2.630 and BAC: 0.065) and Artist Search Task Not Occuring")

barplot(table(soberEventOccur$Combined.Item.Name)/nrow(soberEventOccur)*100, ylim=c(0,100), ylab = "Percent", xlab = "object index number", main = "Sober and Artist Search Task Occuring")

barplot(table(soberEventNotOccur$Combined.Item.Name)/nrow(soberEventNotOccur)*100, ylim=c(0,100), ylab = "Percent", xlab = "object index number", main = "Sober and Artist Search Task Not Occuring")
```

### Examining saccade data
```{r}
sum(drunkEventNotOccur$Saccade == 1) / nrow(drunkEventNotOccur)
sum(drunkEventOccur$Saccade == 1) / nrow(drunkEventOccur)
sum(soberEventOccur$Saccade == 1) / nrow(soberEventOccur)
sum(soberEventNotOccur$Saccade == 1) / nrow(soberEventNotOccur)
```

### Gathering gaze info
```{r}
gazinginfodrunkEventOccur= getGazeInfo(as.character(drunkEventOccur$Combined.Item.Name))
gazinginfodrunkEventOccur = filter(gazinginfodrunkEventOccur, objs != "Nothing")

gazinginfodrunkEventNotOccur= getGazeInfo(as.character(drunkEventNotOccur$Combined.Item.Name))
gazinginfodrunkEventNotOccur = filter(gazinginfodrunkEventNotOccur, objs != "Nothing")

gazinginfosoberEventOccur= getGazeInfo(as.character(soberEventOccur$Combined.Item.Name))
gazinginfosoberEventOccur = filter(gazinginfosoberEventOccur, objs != "Nothing")

gazinginfosoberEventNotOccur= getGazeInfo(as.character(soberEventNotOccur$Combined.Item.Name))
gazinginfosoberEventNotOccur = filter(gazinginfosoberEventNotOccur, objs != "Nothing")
```

### Examining gaze info summary statistics
```{r}
summary(gazinginfodrunkEventOccur)
summary(gazinginfodrunkEventNotOccur)
summary(gazinginfosoberEventOccur)
summary(gazinginfosoberEventNotOccur)
```
Different average gaze lengths could suggest that different attention strategies were employed. Longer average gaze lengths could suggest that the participant was diverting their attention for longer uninterrupted intervals. 

### Examining gaze length distributions
```{r}
boxplot(gazinginfodrunkEventOccur$lens, ylab="Gaze Length Time", main = "Intoxicated (THC:2.630 and BAC: 0.065) and Artist Search Task Occuring") 
boxplot(gazinginfodrunkEventNotOccur$lens, ylab="Gaze Length Time", main = "Intoxicated (THC:2.630 and BAC: 0.065) and Artist Search Task Not Occuring") 
boxplot(gazinginfosoberEventOccur$lens, ylab="Gaze Length Time", main = "Sober and Artist Search Task Occuring") 
boxplot(gazinginfosoberEventNotOccur$lens, ylab="Gaze Length Time", main = "Sober and Artist Search Task Not Occuring")

boxplot(gazinginfodrunkEventOccur$lens, at = 1, xlim = c(0.5, 4.5), ylim = c(0,30), boxcol="red", medcol = "red", ylab="Gaze Length Time", main = "Gaze Length Time over Different Dosages and the Artist Search Task")
boxplot(gazinginfodrunkEventNotOccur$lens, at = 2, add = TRUE, boxcol="blue", ylim = c(0,30), medcol = "blue") 
boxplot(gazinginfosoberEventOccur$lens, at = 3, add= TRUE, boxcol="green", ylim = c(0,30), medcol = "green") 
boxplot(gazinginfosoberEventNotOccur$lens, at = 4, add = TRUE, ylim = c(0,30) ) 
```














